Growing Up With Nell: A Narrative Interface for Literacy

### 2012-04-24 paper.tex
Fix an overfull hbox in the categories list.
Use underline for emphasis in italicized text, instead of lack-of-italics.
Rewrite figure 2 caption to address reviewer's comments (ie, define "JSON").

% A category with the (minimum) three required fields
\category{K.3.1}{Computers and Education}{Computer
  Uses in Education}[computer-managed instruction]
%\category{I.2.7}{Artificial Intelligence}{Natural Language
%  Processing}[narrative interfaces]
\category{H.5.2}{Information Interfaces and Presentation}{User
  Interfaces}[narrative interfaces]
\terms{Design, Human Factors}

@@

\emph{``Good work!  I see a little red \underline{here}.  Can you find
something \emph{big} and red?''}
% avoid excessive/unmerited praise
% try to say *what* you like, rather than just vague praise
% provide quality feedback, encourage the kid to max out the meter on
% their own (ie, making the kid proud of himself for doing well is
% better than telling him they're doing well)

@@

\subsection{Rule-based story modules}
\begin{figure}\small
\begin{verbatim}
{ "world": { // id gives canonical URL for this module
    "id": "/nell.laptop.org/chapters/alphabet-book",
    "scene": "opening", // initial scene
    "inherit_from": "/nell.laptop.org/core/drawing_activity",
  }, "scenes": [
    { "id": "opening", subject: "actors/princess",
      "verb": "speak", object: "actors/user",
      "text": "Hello! Would (o/2) like to hear a story?",
      "group": "/nell.laptop.org/core/story-intro-group",
    },
    { "id": "story-1",
      "cond": rule`At(opening) && Event(Chat, Yes)`,
      "subject": "actors/princess",
      "verb": "speak", object: "actors/user",
      "text": "Once upon a time..." },
    ...
    { "id": "r-drawn",
      "cond": rule`Event(Activity, DrawR)`,
      "subject": "actors/princess",
      "verb": "speak", object: "actors/user",
      "text": "Very good, (o/3)!",
      "action": js`startAnimation("r-runs")` }, ...
  ], ... }
\end{verbatim}
\caption{Excerpt of story module.  JSON syntax has been extended with
quasiquote~\cite{quasiquote}.}\label{fig:rules}
\end{figure}
To implement Nell's modular narrative interface, we use a
production rule system with programmable conflict resolution.
Figure~\ref{fig:rules} shows
an excerpt of the story module underlying the interaction described in
Section~\ref{sec:lesson}.

>>>>

% A category with the (minimum) three required fields
%\category{I.2.7}{Artificial Intelligence}{Natural Language
%  Processing}[narrative interfaces]
\category{H.5.2}{Information Interfaces and Presentation}{User
  Interfaces}[narrative interfaces]
\category{K.3.1}{Computers and Education}{Computer
  Uses in Education}[computer-man\-aged instruction]
\terms{Design, Human Factors}

@@

\emph{``Good work!  I see a little red \underline{here}.  Can you find
something \underline{big} and red?''}
% avoid excessive/unmerited praise
% try to say *what* you like, rather than just vague praise
% provide quality feedback, encourage the kid to max out the meter on
% their own (ie, making the kid proud of himself for doing well is
% better than telling him they're doing well)

@@

\subsection{Rule-based story modules}
\begin{figure}\small
\begin{verbatim}
{ "world": { // id gives canonical URL for this module
    "id": "/nell.laptop.org/chapters/alphabet-book",
    "scene": "opening", // initial scene
    "inherit_from": "/nell.laptop.org/core/drawing_activity",
  }, "scenes": [
    { "id": "opening", subject: "actors/princess",
      "verb": "speak", object: "actors/user",
      "text": "Hello! Would (o/2) like to hear a story?",
      "group": "/nell.laptop.org/core/story-intro-group",
    },
    { "id": "story-1",
      "cond": rule`At(opening) && Event(Chat, Yes)`,
      "subject": "actors/princess",
      "verb": "speak", object: "actors/user",
      "text": "Once upon a time..." },
    ...
    { "id": "r-drawn",
      "cond": rule`Event(Activity, DrawR)`,
      "subject": "actors/princess",
      "verb": "speak", object: "actors/user",
      "text": "Very good, (o/3)!",
      "action": js`startAnimation("r-runs")` }, ...
  ], ... }
\end{verbatim}
\caption{Story module excerpt written in JSON
  (\texttt{http://json.org}) extended with
 quasiquote~\cite{quasiquote}.}\label{fig:rules}
\end{figure}
To implement Nell's modular narrative interface, we use a
production rule system with programmable conflict resolution.
Figure~\ref{fig:rules} shows
an excerpt of the story module underlying the interaction described in
Section~\ref{sec:lesson}.
